Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-16 semantic-nd/article.tex
Big changes on the related work area.
Now it shows related work on the area of using semantic data and graphical
models to model room classification and shows some insights on work performed
on novelty detection area.

Due to unknown and dynamic nature of the operating environment of the agent the
mapping methods should be resilient to new room categories it has never seen
before. This is: perform novelty detection on the concepts the agent is aware of.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
\cite{quattoni2009recognizing} showed that most scene recognition models work poorly
in indoor scenes when compared to outdoor scenes results since the properties that
characterize rooms changes conforming its category. Namely corridors are well
described by global properties and bookstores are well described by the presence of
specific objects (books). Their work shows a multi-modal approach is expected to
yield better performance by mixing several sources of information.

\cite{galindo2005multi} defines a bidirectional relation between object and room
category, where object defines a room category and a room category provides
information on where objects may be found.

Probabilistic representations are used in several localised functions in robots
operating in the real-world~\cite{gross2009toomas,maierprobabilistic}.
And some employ, up to some extent, a probabilistic representation across some
subsystems~\cite{kraft2008exploration}.
And \cite{boutell2006factor} have studied outdoor scene classification using
\emph{factor graphs} and modelling spatial relations between objects in the scene
to extract better knowledge from semantic (high-level) features.

% Its expected that using a unified probabilistic model from the whole system,
% such as \cite{pronobis2011exploiting}, more information can be reused to correctly
% predict a given random variable.

Although this paper deals with novelty detection on the robotics area, it does so
using standard concepts and techniques such as semantic data and graphical models.
Those are often found on areas related with information retrieval.
An interesting example is the work in automatic image annotation using an hidden
concept layer between visual features and text information by \cite{zhang2005probabilistic}.

@@

% Explain threshold approach to novelty detection
Due to the desire of robustness and generalization, a novelty detection system would
always possess some threshold that describes on how strict the system should be to
new data.
This threshold describes a trade of between generalization and certainty.
And is often seen as a distance measure to the known class.

>>>>

Due to the unknown and dynamic nature of the operating environment the
mapping methods should be resilient to new room categories the agent has never seen
before. This is: perform novelty detection on the concepts the agent is aware of.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
The usage of multi-modal approaches, such as combining semantic data extracted from
several sources or classifiers is expected to have better performance on scene
recognition than single approaches according to \cite{quattoni2009recognizing}
that showed that most scene recognition models work poorly in indoor scenes when
compared to outdoor scenes results since the properties that
characterize rooms changes conforming its category. Namely corridors are well
described by global properties and bookstores are well described by the presence of
specific objects (books).
\cite{galindo2005multi} also exploits this by defining a bidirectional relation
between object and room category, where object defines a room category and a room
category provides information on where objects may be found.

Probabilistic representations have also been used in several localised functions
in robots operating in the real-world~\cite{gross2009toomas,maierprobabilistic}.
And some employ, up to some extent, a probabilistic representation across some
subsystems~\cite{kraft2008exploration}.
And \cite{boutell2006factor} have studied outdoor scene classification using
\emph{factor graphs} and modelling spatial relations between objects in the scene
to extract better knowledge from semantic (high-level) features.

Also although this paper deals with robotics area, it does so
using standard concepts and techniques such as semantic data and graphical models.
Those are often found on areas related with information retrieval.
An interesting example is the work in automatic image annotation using an hidden
concept layer between visual features and text information by \cite{zhang2005probabilistic}.

Novelty detection has been studied for some years and there is several approaches
based on statistical analysis as reported by \cite{markou2003novelty}.
Graphical models have been used to learn distributions of variables, both in
supervised and unsupervised ways and by using thresholds on those distributions
based solely on the conditional probability as seen on \cite{bishop1994novelty}
a novelty system can be trivially implemented.
But as far as we known there is no reference on how to perform novelty detection
by using graphs that are dynamically generated.

@@

% Explain threshold approach to novelty detection
Due to the desire of robustness and generalization, a novelty detection system would
always possess some threshold that describes on how strict the system should be to
new data.
This threshold describes a trade between error and rejection.
And is often seen as a distance measure to the known class.
